Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-08 mu/article/article.tex
Correction of descriptions when velocity is fixed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%  I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%                          %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
\begin{equation}
\dot{K} = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation}
where
\begin{widetext}
\begin{equation}
\mu^{\mathrm{abcd}} (\omega) =
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
r^{\mathrm{d}}_{vc'} 
r^{\mathrm{c}}_{cv } ) \right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
\end{equation}
\end{widetext}
is the corresponding spin density injection current pseudotensor. The $'$
in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}
% 
\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

@@

Using the ABINIT code \cite{gonzeCPC09} we calculated the self- consistent
ground state and the Kohn-Sham states using density functional theory in the
local density approximation (DFT-LDA) with a planewave basis. We used
Hartwigsen- Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
for calculating $\mathcal{V}^{\mathrm{a}}(\omega)$.

The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were
calculated using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the
irreducible Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV
and 0.088\,eV, respectively for the \emph{alt} and \emph{up} structures. As
mentioned in
\cite{zapataPSB2016}, using DFT the LDA is only one method of many other that
can be used to calculate the electronic structure of materials. Also it is
known that all methods predict a different band gap than the obtained in the
experiment. A correction for the band gap energy value can be calculated by
other \emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02}
being this outside the scope of this paper.

@@

\subsection{Spin velocity} % (fold)
\label{sec:res-pure_spin_current_and_spin_velocity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{plots/vab-str-comp}
    \caption{Comparison of most intense responses for
    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs
    structures}
    \label{fig:vab-str-comp}
\end{figure}

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is hold
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the 2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\hline
Kind of  & 
\multirow{2}{*}{\quad Structure \quad} & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
system & & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\hline
2D   & \emph{up}    & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
     &              &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
     &              &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\hline
2D   & \emph{alt}   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
     &              &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
\hline
bulk &  CdSe        & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
\hline
bulk &  GaAs        & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\hline
\end{tabular}
\caption{Comparison of the reported maxima values of $\mathcal{V}^{\mathrm{ab}}$
for different structures and the corresponding polarization angle $\alpha$ and energy
values.}
\label{tab:vab-str-comp}
\end{table}

@@

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\blindtext
\blindtext

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Up structure.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% I N T R O D U C T I O N %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%                         %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

{\color{red}
\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
\begin{equation}
\dot{K} = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation}
where
\begin{widetext}
\begin{align}
\mu^{\mathrm{abcd}} (\omega) 
&=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
r^{\mathrm{d}}_{vc'} 
r^{\mathrm{c}}_{cv } ) \right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
\\
K^{\mathrm{ab}}_{mn}
&=
\sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
\label{eq:velspi-matelem}
\end{align}
\end{widetext}
is the corresponding spin density injection current pseudotensor. The $'$
in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
} % COLOR RED END
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta_{\mathrm{a}}  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Theory: Layer by layer %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\color{red}
\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

@@

\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}

\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}
% 
\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
\quad Layer \quad & \quad Atom \qquad & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
\quad No.   \quad & \quad type \qquad & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}

\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

@@

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
\textcolor{red}{ needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}) and $|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vab}).}
%
{\color{red} 
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other \emph{ab-
initio} methods such as the GW approximation \cite{onidaRMP02} but this is
outside the scope of this paper.
} % COLOR RED END
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

{\color{red}

\subsection{Spin velocity} % (fold)
\label{sec:res-spin_velocity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{plots/vab-str-comp}

    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
    polarization angles.}
    \label{fig:vab-str-comp}
\end{figure}

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
             &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
 CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
 GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\end{tabular}

\caption{\color{red} Comparison of the reported maxima values of
$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
polarization angle $\alpha$ and energy values.}
\label{tab:vab-str-comp}
\end{table}
} % COLOR RED END

@@

% \subsection{Fixing spin} % (fold)
% \label{sec:res-fixspin}

% \blindtext

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{figure}[t]
%     \centering
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsx-1}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-1}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsy-1}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-1}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsz-1}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}

%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
%     structure.}
%     \label{fig:up-3d-vsb-1}
% \end{figure}

% \begin{figure}[t]
%     \centering
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsx-2}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svax-2}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsy-2}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svay-2}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{up} structure 
%     \label{fig:up-3d-vsz-2}]
%     {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}

%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for the \emph{up}
%     structure.}
%     \label{fig:up-3d-vsb-2}
% \end{figure}

% \begin{figure}[t]
%     \centering
%     \subfigure[\, \label{fig:up-vaz-rag-1}]
%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
%     \\
%     \subfigure[\, \label{fig:up-vaz-rag-2}]
%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
%     \emph{up} structure.}
%     \label{fig:up-vaz-rag}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{figure}[t]
%     \centering
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$ for \emph{alt} structure 
%     \label{fig:alt-3d-vsx}]
%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svax}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$ for \emph{alt} structure 
%     \label{fig:alt-3d-vsy}]
%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svay}}
%     \\
%     \subfigure[\ $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ for \emph{alt} structure 
%     \label{fig:alt-3d-vsz}]
%     {\includegraphics[width=\linewidth]{altplots/alt-3d-svaz}}

%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{x}}}|$,
%     $|\mathcal{V}_{\sigma^{\mathrm{y}}}|$, and
%     $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ responses for \emph{alt} structure. }
%     \label{fig:alt-3d-vsb}
% \end{figure}

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
%     \emph{alt} structure.}
%     \label{fig:figure1}
% \end{figure}

% \blindtext

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Up structure.}
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
    range from 0.07\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

    \caption{Most intense response of
    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
